### 2014-03-11 thesis/src/chapters/chapter-implementation.tex
Thesis: fixes part 2

      The reason we chose this technology is because of its simplicity, maturity and great support from Ruby platform. The other solutions that could be used in place of this one include some message-oriented middleware standards such as AMQP or JMS, other standards that facilitate communications among systems/components such as CORBA, and other such as RMI or RPC. Some of the aforementioned technologies had been eliminated once we chose Ruby as the language which the platform would be implemented in. This is because of their platform-specific nature, e.g. JMS requires the system to be written in Java.

@@

  \item Auto-scaling subsystem
    \begin{asparaenum}
    \item[\textbf{OpenNebula}] There was a need for a tool that would be used for efficient management of the resources of a data center. OpenNebula is an open source respond to this need -- first released in 2008, with good support from the community, seemed a good candidate for a tool. Our familiarity with it was an additional factor which influenced our final choice of OpenNebula as the tool for the job.
    \item[\textbf{Chef}] As manual virtual machines provisioning is a tedious and error-prone task, this is a perfect match for a tool that would automate the process. We chose \emph{Chef} as it is written in the language of the whole platform (i.e. Ruby), mature (initially released in 2009) and widely used tool. \footnote{According to the website of the product (\url{http://www.getchef.com/customers/}), it is used by such companies as Facebook, BlueKai or BookRenter. More can be found at the provided URL.}
    \item[\textbf{OpenVZ (drivers)}] The significance of choosing linux containers as a virtualisation technology was fully described in the preceding chapters. However, the drivers for the OpenVZ are not supported by the OpenNebula maintainers, so we had to use our own-developed tool while taking a course at the university. This tools forms an official add-on for OpenNebula 3.8.
    \end{asparaenum}
\end{itemize}

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/csap-cloud-brokerage-deployment-diagram}
  \end{center}
  \caption{Deployment diagram of a Cloud brokerage subsystem}
  \label{fig:csap-cloud-brokerage-deployment-diagram}
\end{figure}

\subsection{Cloud client}
The client is a command line application that allows a user to communicate with a cloud broker which will further process the message and act on behalf the user. By means of this application, the user is able to deploy a service by preparing its specification in a JSON format and request its deployment to the cloud broker. Listing \ref{lst:service-spec-test-deployment-time} is an example of a service description.

@@

The broker uses Advanced Message Queuing Protocol (AMQP) for communication between itself and cloud providers. It was considered the best choice for this purpose as it ensure asynchronous message processing and sending messages according to fan-out paradigm which is ideal for this use case.

@@

\subsubsection{Cloud providers selection}
One of the main responsibilities of the Cloud broker is to map the stacks of a given service to cloud providers. This happens when a service is to be deployed or horizontally scaled. As this implementation merely wants to be a minimal viable product, we took only the cost attribute into consideration when performing this function.

@@

  This manager creates an offer for a service that consists of the cost of each stack. This cost is not dynamically computed, but fetched from the configuration file that contains mapping between the stack and its cost. The offer is sent back to the cloud broker for further processing.
\item[\textbf{Horizontal-scaling message}] This message is send when it is not possible to continue having deployed a stack on the given cloud instance by the lack of sufficient resources or violation of a policy. It contains the stack specification as the platform needs this information to redeploy the stack to another cloud instance.
\end{asparaenum}

>>>>

      The reason why we chose this technology is because of its simplicity, maturity and great support from Ruby platform. The other solutions that could be used in place of this one include some message-oriented middleware standards such as AMQP or JMS, other standards that facilitate communications among systems/components such as CORBA, and other such as RMI or RPC. Some of the aforementioned technologies had been eliminated once we chose Ruby as the language which the platform would be implemented in. This is because of their platform-specific nature, e.g. JMS requires the system to be written in Java.

@@

  \item Auto-scaling subsystem
    \begin{asparaenum}
    \item[\textbf{OpenNebula}] There was a need for a tool that would be used for efficient management of the resources of a data center. OpenNebula is an open source respond to this need -- first released in 2008, with good support from the community, seemed a good candidate for a tool. Our familiarity with it was an additional factor which influenced our final choice.
    \item[\textbf{Chef}] As manual virtual machines provisioning is a tedious and error-prone task, this is a perfect match for a tool that would automate the process. We chose \emph{Chef} as it is written in the language of the whole platform (i.e. Ruby), mature (initially released in 2009) and widely used tool. \footnote{According to the website of the product (\url{http://www.getchef.com/customers/}), it is used by such companies as Facebook, BlueKai or BookRenter. More can be found at the provided URL.}
    \item[\textbf{OpenVZ (drivers)}] The significance of choosing linux containers as a virtualisation technology was fully described in the preceding chapters. However, the drivers for the OpenVZ are not supported by the OpenNebula maintainers, so we had to use our own-developed drivers while taking a course at the university. They form an official add-on for OpenNebula 3.8.
    \end{asparaenum}
\end{itemize}

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/csap-cloud-brokerage-deployment-diagram}
  \end{center}
   \caption{Deployment diagram of cloud brokerage subsystem}
  \label{fig:csap-cloud-brokerage-deployment-diagram}
\end{figure}

\subsection{Cloud client}
The client is a command line application that allows a user to communicate with a cloud broker which will further process the message and act on the user behalf. By means of this application, the user is able to deploy a service by preparing its specification in a JSON format and request its deployment to the cloud broker. Listing \ref{lst:service-spec-test-deployment-time} is an example of a service description.

@@

The broker uses Advanced Message Queuing Protocol (AMQP) for communication with cloud providers. It was considered the best choice for this purpose as it ensures asynchronous message processing and sending according to fan-out paradigm which is ideal for this use case.

@@

\subsubsection{Cloud providers selection}
One of the main responsibilities of the Cloud broker is to map the stacks of a given service to cloud providers. This happens when a service is to be deployed or horizontally scaled. As this implementation merely wants to be a minimal viable product, we took only the cost into consideration when performing this function.

@@

  This manager creates an offer for a service that consists of the cost of each stack. This cost is not dynamically computed, but fetched from the configuration file that contains mapping between the stack and its cost. The offer is sent back to the cloud broker for further processing.
\item[\textbf{Horizontal-scaling message}] This message is send when it is not possible to continue scaling of deployed a stack on the given cloud instance due to the lack of sufficient resources or violation of a policy. It contains the stack specification as the platform needs this information to redeploy the stack to another cloud instance.
\end{asparaenum}

### 2014-03-11 thesis/src/chapters/chapter-summary.tex
Thesis: fixes part 2

Having more mature platform implemented and tested, next step should be to engage communities working on Open Source cloud platform such as OpenNebula, OpenStack or Eucalyptus. It is expected that such cooperation broaden pool of supported cloud providers and thus truly enable diversified federation of clouds. However, for cloud providers to cooperate, there is a need for discussion and consideration regarding aspects such as authentication, authorization, resource
 access, resource discovery, to name a few.

>>>>

Having more mature platform implemented and tested, next step should be to engage communities working on Open Source cloud platform such as OpenNebula, OpenStack or Eucalyptus. It is expected that such cooperation broaden pool of supported cloud providers and thus truly enable diversified federation of clouds. However, for cloud providers to cooperate, there is a need for discussion and consideration regarding aspects such as authentication, authorization, resource access and resource discovery, to name a few.
